---
title: "list column"
author: "Chenxin Zhang"
date: "11/16/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Lists

You can put anything in a list. 
an numeric vector
a logical vector 
matrix

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)
```

```{r}
l
l$vec_numeric
l[[1]] #give me the first list element
l[["vec_numeric"]]
mean(l[["vec_numeric"]])
```

## `for` loop

Create a new list.
abcd is input id name
```{r}
list_norm = 
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(30, mean = 0, sd = 5),
    c = rnorm(40, mean = 10, sd = .2),
    d = rnorm(20, mean = -3, sd = 1)
  )

list_norm$a
list_norm[[1]]
list_norm[["a"]]
```

function.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

**apply that function to each list element**

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

**for loop**

```{r}
output = vector("list", length = 4)
for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
}
```

**map**
given all element in a list to a function

map():result is still a list
```{r}
output = map(list_norm, mean_and_sd)
output = map(list_norm, median)#a different function:IQR,
```

map_dbl(): result show up as numbers rather than as lists
```{r}
output = map_dbl(list_norm, median)
output = map_dbl(list_norm, median, .id = "input")#no different from above, so we do not need a id = input in map_dbl
```

map_df(): result is not a list of data frame but a combined data frame
```{r}
#output = map_dbl(list_norm, mean_and_sd) is not correct, result must be a  single double, not a vector of class
output = map_df(list_norm, mean_and_sd)
output = map_df(list_norm, mean_and_sd, .id = "input")
#each output of mean and sd is a tibble
#put list name(abcd) from list_norm into a column named input
```

**List columns**

creat a data frame that has a list column in it

```{r}
# put abcd in a column called 'name'
#'samp' column is the list of samples generated previously
#first row in 'name' has a and the first row in 'samp' has that first element of list_norm(it's a vector of class double of length 20)
#a more compact way of looking things
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm
  )
```

pull element in data frame
```{r}
listcol_df %>% pull(name)#get the first column by pull()
listcol_df %>% pull(samp)#get the second column by pull(), the list
listcol_df$samp[[1]]#get the first element of the list
listcol_df %>% 
  filter(name == "a")#get the first row of the data frame as a tibble 
```

some operations: dataframe-map, function

```{r}
#get the first element in the list
listcol_df$samp[[1]]
# put the first element into a function
mean_and_sd(listcol_df$samp[[1]])
# put the first element into a function
mean_and_sd(list_norm[[1]])


#map accross 'samp' column as an input list by mean_and_sd function
map(listcol_df$samp, mean_and_sd)
map(list_norm, mean_and_sd)
```

**add a list column**

```{r}
#map_df() result as data frame
#map() result as list
listcol_df1 = 
  listcol_df %>% 
  mutate(summary = map_df(samp, mean_and_sd),
         medians = map(samp, median))
```

```{r}
#apply this function to each element of the list and save that output in the same data frame
#mutate function working inside the listcol_df, so we do not need listcol_df$samp
#creat a 'summary' column by map mean_and_sd across the 'samp' column in this data set
#
listcol_df2 = 
  listcol_df %>% 
  mutate(
    summary = map(samp, mean_and_sd),#result as list
    medians = map_dbl(samp, median))# result as single number
```

