---
title: "simulation"
author: "Chenxin Zhang"
date: "11/17/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)#for reproducibility, make our sample start in the same point over and over
```


simulation is do repeated sampling which cannot do in really life

# Let's simulate something

creat a normal distribution data 

```{r}
sim_data = 
    tibble(
      x = rnorm(n = 100, mean = 2, sd = 3)
    )
```

summarize mean and sd

```{r}
sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
```

Creat a function.

```{r}
sim_mean_sd = function(samp_size, mu = 3, sigma = 4) {
  
  sim_data = 
    tibble(
      x = rnorm(n = samp_size, mean = mu, sd = sigma)
    )#generate data from a normal distribution
  sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
  
}
```

I can "simulate" by running this line. 

```{r}
sim_mean_sd(30)
```


## Let's simulate a lot

**for loop**

```{r}
output = vector("list", length = 100)#vector of type list
for (i in 1:100) {
  
  output[[i]] = sim_mean_sd(samp_size = 30)
  
}
bind_rows(output)#not a list but data frame
```

Let's use a loop function.
similar to for loop
```{r}
# rerun the function 100 times
sim_results = 
  rerun(100, sim_mean_sd(samp_size = 30)) %>% 
  bind_rows()
```

Let's look at results...


```{r}
sim_results %>% 
  ggplot(aes(x = mean)) + geom_density()
sim_results %>% 
  summarize(
    avg_samp_mean = mean(mean),
    sd_samp_mean = sd(mean)
  )
sim_results %>% 
  ggplot(aes(x = sd)) + geom_density()
```

## Let's try other sample sizes.

when n=30 run simulation code 100 times
```{r}
n_list = 
  list(
    "n = 30" = 30,
    "n = 60" = 60,
    "n = 120" = 120,
    "n = 240" = 240
  )

output = vector("list", length = 4)
output[[1]] = rerun(100, sim_mean_sd(samp_size = n_list[[1]])) %>% bind_rows()#compute only one time, so we use for loop to simulate many times


for (i in 1:4) {
  output[[i]] = 
    rerun(100, sim_mean_sd(samp_size = n_list[[i]])) %>% 
    bind_rows()
}#finally get 4 list
```


```{r}
# make a tibble and use mutate to add the result as new column
# maping  sample_size across return(), get a list column
# .x means that the first argument to map is .x; tidle means put the .x to the function; whatever the first sample size is , it is going to get plugged in over the function
sim_results = 
  tibble(
    sample_size = c(30, 60, 120, 240)
  ) %>% 
  mutate(
    output_lists = map(.x = sample_size, ~ rerun(100, sim_mean_sd(.x))))
```

```{r}
#pull the list from column
#in the result : [[1]] means the first element in the output lists is a list, [[1]][[2]]] means the second piece in that list is a tibble
sim_results %>% 
  pull(output_lists)
```



```{r}
# there are 10 lists in the first list, so we combine the 10 list to a tibble
sim_results  %>% 
  mutate(
  estimate_df = map(output_lists, bind_rows)
  ) %>% 
  pull(estimate_df)
```

unnest a data frame
```{r}
sim_results = sim_results  %>% 
  mutate(
  estimate_df = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_df)
```

Do some data frame things.

warning: Continuous x aesthetic in x axis
```{r}
plot1 = sim_results %>% 
  ggplot(aes(x = sample_size, y = mean)) + 
  geom_boxplot()
```

creat an actually informative lable in x axis
```{r}
# overwrite string in sample_size column that is equal to the combination of 'n = ' and the original sample_size
# reorder wahtever in sample size column
plot2 = 
  sim_results %>% 
    mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mean)) + 
  geom_boxplot()
```

violin plot
```{r}
# get a symmetric distribution, when you turn your head to the side each of those looks kind of like a normal distribution
plot3 = 
  sim_results %>% 
    mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mean)) + 
  geom_violin()
```


```{r}
# if you run ten thousand times it should get closer
sim_results %>% 
  group_by(sample_size) %>% 
  summarize(
    avg_samp_mean = mean(mean),
    sd_samp_mean = sd(mean)
  )
```




