---
title: "Writing functions"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)
(x_vec - mean(x_vec)) / sd(x_vec)
```

I want a function to compute z-scores

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}
z_scores(x_vec)
```

Try my function on some other things. These should give errors.

```{r, error = TRUE}
z_scores(3) #
z_scores("my name is jeff")#cannot be a character
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```

## Multiple outputs
two things need to return, so we do not use return() but tibble/list
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Check that the function works.

```{r}
x_vec = rnorm(100, mean = 3, sd = 4)
mean_and_sd(x_vec)
```

## Multiple inputs

**usuall way** 

```{r}
sim_data =
  tibble(
    x = rnorm(100, mean = 6, sd = 3)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

**I'd like to do this with a function. **
use mu but not mean because we use true mean
sim_mean_sd = function(n, mean,sd)
the imput mu will bw drop into mean = mean(x)
run this function, each time you will get different mean and sd

```{r}
sim_mean_sd = function(samp_size, mu, sigma){
  
  sim_data =
  tibble(
    x = rnorm(n = samp_size, mean = mu, sd = sigma)
  )
  
  sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}

sim_mean_sd(100,6,3)#can not shif name
sim_mean_sd(samp_size = 100, mu = 6, sigma = 3)#recomand use name to match in function
sim_mean_sd(mu = 6, samp_size = 100, sigma = 3)#can shif things with name defined
```

when the defult value is defined:
sim_mean_sd_d = function(samp_size, mu = 3,sigma = 4)
you can replace the defult with our prefer



## Let's review Napoleon Dynamite
**gather amazon review as data**
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1" #this is only page 1 in the website

dynamite_html = read_html(url)

review_titles =
  dynamite_html %>% 
  html_nodes(".a-text-bold span") %>% 
  html_text() # convert to text

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>% #get the first(^) digits(d),^is a special charactor which require \, and \ itself is a charactor which need \
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% #until this step you get \n in the begining and end of each review
  str_replace_all("\n", "") %>% #replace \n with nothing
  str_trim() # trimming off the two white spaces in the beginning


reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```



**if you want to get more pages**
given url and read url,you can give x and read x 

```{r}

read_page_reviews = function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  reviews = 
    tibble(
      title = review_titles,
      stars = review_stars,
      text = review_text
    )
  
  reviews
  
}
```

Let me try my function.

```{r}
dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"
read_page_reviews(dynamite_url)
```

**Let's read a few pages of reviews** 

```{r}
dynamite_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=" #get a url base the number is not specified
dynamite_urls = str_c(dynamite_url_base, 1:5) #combine url base with number 1-5

all_reviews = 
  bind_rows(
    read_page_reviews(dynamite_urls[1]),#read page reviews on the first page
    read_page_reviews(dynamite_urls[2]),
    read_page_reviews(dynamite_urls[3]),
    read_page_reviews(dynamite_urls[4]),
    read_page_reviews(dynamite_urls[5])
  )
```

## Mean scoping example

f = function(x) {
  z = x + y
  z
}
x = 1
y = 2
f(x = y)


## Functions as arguments


my_summary = function(x, summ_func) {
  
  summ_func(x)
  
}
x_vec = rnorm(100, 3, 7)
mean(x_vec)
median(x_vec)
my_summary(x_vec, IQR)


