---
title: "Writing functions"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)
(x_vec - mean(x_vec)) / sd(x_vec)
```

I want a function to compute z-scores

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}
z_scores(x_vec)
```

Try my function on some other things. These should give errors.

```{r, error = TRUE}
z_scores(3) #
z_scores("my name is jeff")#cannot be a character
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```

## Multiple outputs
two things need to return, so we do not use return() but tibble/list
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Check that the function works.

```{r}
x_vec = rnorm(100, mean = 3, sd = 4)
mean_and_sd(x_vec)
```

## Multiple inputs

**usuall way** 

```{r}
sim_data =
  tibble(
    x = rnorm(100, mean = 6, sd = 3)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

**I'd like to do this with a function. **
use mu but not mean because we use true mean
sim_mean_sd = function(n, mean,sd)
the imput mu will bw drop into mean = mean(x)
run this function, each time you will get different mean and sd

```{r}
sim_mean_sd = function(sample_size, mu,sigma){
  
  sim_data =
  tibble(
    x = rnorm(sample_size, mean = mu, sd = sigma)
  )
  
  sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}

sim_mean_sd(100,6,3)#can not shif name
sim_mean_sd(samp_size = 100, mu = 6, sigma = 3)#recomand use name to match in function
sim_mean_sd(mu = 6, samp_size = 100, sigma = 3)#can shif things with name defined
sim_mean_sd(samp_size = 100)
```

when the defult is defined
```{r}
sim_mean_sd = function(sample_size = 100, mu = 3,sigma =3){
  
  sim_data =
  tibble(
    x = rnorm(sample_size, mean = mu, sd = sigma)
  )
  
  sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}
sim_mean_sd(100,6,3)#replace the defult with our prefer
```

